Manuscript drafts

### 2020-03-10 manuscript/drafts/manuscript.Rmd
- add condition grid - add background on other strategies - add starting point, retraining, querying

RQ1

## active learning for systematic reviews 
achine learning algorithms cannot predict the relevance of abstracts from the raw texts as they are. 
The content of the texts needs to be transformed into numerical representations. The processs of transforming texts to numerical feature vectors is called word embeddings.

A classical example of word embeddings is 'bag of words'. For each each text, the number of occurrences of each word is stored. This leads to n features, where n is the number of distinct words in the texts. [@scikit-learn]

Word embeddings allows ASReview to predict relevance of abstracts from the features of abstracts of which relevance is known.

corpus = all the text:

ASReview implements several feature extraction strategies. The following will be compared:

The model is typically a learning algorithm used to predict the relevance of text.

@@

## Background
[@Yu2018a], [@Yu2019] simulated 32 svm classifiers, on software engineering. 
A popular classifier is SVM 
In terms of Yu et al, we adopt .CT.

@@

## Datasets

The algorithm will be tested on five systematic reviews from various research areas. 
test datasets serve as systematic search results, then perform active learning to detect inclusions.

@@

## Models 
Now, we build five different active learning models.

we have a model $M$ using a classifier $c$ with (hyper)parameters $h$, performing an automated systematic review on SR dataset $d$.

We are going to test 5 models on 5 different datasets.

classifier - feature extraction - query strategy - balance strategy

BTMD -

#### Classifiers
- Naive Bayes (B)
- Random Forests (R)
- Support Vecor Machine (S)
- Logistic Regression (L)
- Dense Neural Network (N)

#### Feature extraction strategies
To compute relevancy of a paper, we use the title and abstract 
- baseline model:

### Balance strategies
triple = 
The other parameters remain fixed over the 5 models:

- Query Strategy = max
- Balance Strategy = triple
- n_instances=10 (number of papers each query)
- n_prior_included = 5
- n_prior_excluded = 5

## Simulations
The original systematic review is reproduced using five different models.

A simulation is of one model on one dataset.

The model starts with 5 inclusions and 5 exclusions, randomly selected. The simulation is repeated for 10 trials $t$. 
We use 5 inclusions and exclusions as we assume the researcher has some prior knowledge on this. 
The researcher has some prior knowledge about the pool, some papers ought to be included in the SR
for every for every model (5), for every dataset (5) and for every set of optimized hyperparameters (3), a simulation study consisting trials is performed. From these $5*5*3=75$ simulation studies, performance of the different models is evaluated.

Every simulation study consists of 10 trials, to account for the randomness of prior inclusions and exclusions. Results are aggregated (?)

assumptions

@@

### Optimizing Hyperparameters 
Every model has its own hyperparameters. 
For every model, the hyperparameters are optimized three times, arriving at three versions of the model:

@@

# Performance metrics
Tradeoff: identifying all relevant papers and reducing workload.

>>>>

## active learning for systematic reviews 
corpus = all the text:

@@

RQ1 - what are good classifiers 
RQ2 - what are good optimization strategies

## Background
[@OMara-Eves2015] literature review

[@Yu2018a], [@Yu2019] simulated 32 svm classifiers, on software engineering. 
A popular classifier is SVM. succes with HUTM (fastread), uncertainty, mix of weighting and agressive undersampling, 
In terms of Yu et al, we adopt .CT.

SVM - tf-idf on medical data, uncertainty sampling, agressive undersampling. [@Wallace2010]

abstrackr

SVM + Weighting + uncertainty (bow) produced good methods  [@Miwa2014]
Also include social sciences data besides medical data.

[@Cohen2006] perceptron-based classifier (neural network)

SVM on legal documents (no balancing, certainty ) [@Cormack2014] 
in limitations section mentions that LR yields about same results, nb inferior results.

[@Kilicoglu2009] - SVM, naive bayes, boosting and combinations. future work should optimize parameters.
  "Regarding the base classifiers used in identifying method- ologically rigorous studies, boosting consistently strikes the best balance between precision and recall, whereas Naïve Bayes in general performs well on recall (demonstrating a tradeoff between recall and precision), as does polynomial SVM on precision. The AUC results are mixed, although boosting has a slight edge overall. These results demonstrate that different classifiers can be used to satisfy different information needs (SVM for specificity, Naïve Bayes for sensitivity, and boosting for balance between the two, for example)."

@@

## Datasets
The algorithm will be tested on five systematic reviews from various research areas. 
test datasets serve as systematic search results, then perform active learning to detect inclusions.

@@

There are two classes in the data: exlusions and inclusions.
The inclusions are clearly the minority class.

## Models 
Five different active learning models were build. 
Every model $m$ was used to perform an automated systematic review on SR dataset $d$. 
The models all apply a different classifier $c$ with its own set of (hyper)parameters $h$.

#### Classifiers
The classifier predicts the class of all papers. 
To predict whether a paper should be an exclusion or an inclusion, different classifiers

- Naive Bayes (B)
- Random Forests (R)
- Support Vecor Machine (S)
- Logistic Regression (L)
- Dense Neural Network (N)

Besides $c$, components of $m$ are fea

To summarize, every model $m$ consists of the following key components: 
classifier, feature extraction strategy, query strategy, balance strategy.

For example $M_1$ BTMD (naive bayes, tfidf, certainty sampling, double balance)
STMD

#### Word representation 
To be able to predict whether a paper needs to be included or excluded (e.g. to predict class), 
the classifier needs some features from the papers.  
As features we use the title and abstract from every paper - this is what is prescribed by prisma, (check!) 
The classifier cannot predict the paper class from the raw titles and abstracts as they are.
Therefore, the content of the texts needs to be transformed into numerical representations called feature vectors.

A classical example is a 'bag of words' representation. 
For each each text, the number of occurrences of each word is stored. 
This leads to n features, where n is the number of distinct words in the texts [@scikit-learn].

We use the following feature extraction methods
- TF-IDF

#### The next abstract to be queried  
The model has various ways of deciding which instance should be queried next.

#### Rebalancing the training set
To account for class imbalance in the data, the model can apply several strategies to rebalance the training set.

A reweighting strategy is applied where inclusions (the minority class) are weighted more heavily than the exclusions.

#### Starting point
The initial training set consists of 5 inclusions and 5 exclusions, randomly sampled from the dataset. 
We use 5 inclusions and exclusions as we assume the researcher has some prior knowledge on this. 
The researcher has some prior knowledge about the pool, some papers ought to be included in the SR.

```
c = naivebayes
f = tfidf
q = max
n_prior_included = 5
n_prior_excluded = 5
```

#### Retraining
We can choose to retrain the model after labeling $n$ instances. 
- n_instances=10 (number of papers each query)

## Simulations
To evaluate performance of the five models described above, the model is used to simulate five existing systematic reviews.

### Optimizing hyperparameters
For every model*data combination, 3 sets of hyperparameters are generated to ... 
parallel
Every model has its own hyperparameters. 
For every model, the hyperparameters are optimized three times, arriving at three versions of the model:

We nog have 75 combinations. 
for every for every model (5), for every dataset (5) and for every set of optimized hyperparameters (3), a simulation study consisting trials is performed. From these $5*5*3=75$ simulation studies, performance of the different models is evaluated.

A simulation is of one model on one dataset. 
The simulation is repeated for 10 trials $t$.

Every simulation study consists of 10 trials, to account for the randomness of prior inclusions and exclusions.
So every trial the prior inclusions and exclusions are randomly selected. 
Results are aggregated (?)

#### Assumptions

@@

@@

# Performance metrics
The goal is twofold: we want to identify all relevant papers, as fast as we can. 
Tradeoff: identifying all relevant papers and reducing workload. 
A good metric to evaluate this is..
